---
title: "Figure 5b"
author: "David Bradley"
date: "1/1/2021"
output: html_document
---

# GGplot font

```{r}

# https://stackoverflow.com/questions/27689222/changing-fonts-for-graphs-in-r

library(extrafont)

font_import()
loadfonts()       #Register fonts for Windows bitmap output
fonts() 

```

# The first step is to model the specificity of CK2

```{r}

library(stringr)
library(readr)
library(seqinr)
library(ggseqlogo)
library(gdata)

# Data comes from Bachmann et al., 2019 (https://www.biorxiv.org/content/10.1101/822668v3)

prot_mapper <- read_csv('export.csv')

# Kinases only

prot_mapper <- prot_mapper[unlist(prot_mapper[,5]) == TRUE,]

# Retrieve upstream kinase, substrate, and substrate position

ksr <- prot_mapper[,c(3,4,6,9,10)]

# We exclude KSRs that are supported only by the text-mining tools

curated <- c('psp','signor','pid','bel','reactome')

source_list <- strsplit(unlist(ksr[,5]),split=',')

number_curated <- lapply(source_list, function(x) length(intersect(x,curated)))

ksr <- ksr[which(number_curated > 0),]

# Correct formatting problems

for (i in 1:nrow(ksr)) {
 
  if(is.na(ksr[i,2])) {ksr[i,2] <- ksr[i,1]} 
  
}

# Retrieve CSNK2A1 and CSNK2A2 substrates

csnk2a1_ksr <- ksr[which(unlist(ksr[,2] == 'CSNK2A1') == TRUE),]
csnk2a2_ksr <- ksr[which(unlist(ksr[,2] == 'CSNK2A2') == TRUE),]
csnk2a_ksr <- unique(rbind(csnk2a1_ksr,csnk2a2_ksr)) 

hs_rp <- read.fasta('hs_proteome_uniprot.fasta', seqtype='AA')
hs_ids <- rapply(strsplit(names(hs_rp),split='\\|'),function(x) x[2])

# Retrieve the flanking sequences of the phosphosites

psite_vec <- NULL
index_vec <- NULL

for (i in 1:nrow(csnk2a_ksr)) {
  
  print(i)
  
  # Retrieve the first element only
  uniprot_id <- unname(unlist(csnk2a_ksr[i,3]))
  site_pos <- unname(unlist(csnk2a_ksr[i,4]))
  
  # Loop for ambiguous psite positions
  
  for (j in 1:length(uniprot_id)) {
    
    pos <- as.numeric(site_pos)
    
    # Substrate sequence
  
    sub_seq <- unlist(getSequence(hs_rp[hs_ids %in% uniprot_id[j]]))
    
    if (length(sub_seq) == 0) {next}
    
    # Phosphosite position
    
    if (pos < 8) {
      
      gap <- paste(rep('_',(8-pos)),collapse='')
      psite <- paste(sub_seq[1:(pos+7)],collapse='')
      psite <- paste(gap,psite,sep='')
      if (!substr(psite,8,8) %in% c('S','T','Y')) {next}
      psite_vec <- c(psite_vec, psite)
      index_vec <- c(index_vec, i)
      
    } else if ((pos+7) > length(sub_seq)) {
      
      psite <- paste(sub_seq[(pos-7):(length(sub_seq))],collapse='')
      gap <- paste(rep('_',(pos+7)-length(sub_seq)),collapse='')
      psite <- paste(psite,gap,sep='')
      if (!substr(psite,8,8) %in% c('S','T','Y')) {next}
      psite_vec <- c(psite_vec, psite)
      index_vec <- c(index_vec, i)
      
    } else {
      
      psite <- paste(sub_seq[(pos-7):(pos+7)],collapse='')
      if (!substr(psite,8,8) %in% c('S','T','Y')) {next}
      psite_vec <- c(psite_vec, psite)
      index_vec <- c(index_vec, i)
      
    }
  } 
}

# Remove potential hierarchical sites
bachmann_vec <- psite_vec
p1s <- rapply(strsplit(psite_vec,split=''), function(x) x[9]) == 'S'
p3s <- rapply(strsplit(psite_vec,split=''), function(x) x[11]) == 'S'
psite_no_heira <- psite_vec[!(p1s|p3s)]

# Bind flanking sequences to the original data frame

csnk2a_ksr <- csnk2a_ksr[index_vec,]
csnk2a_ksr <- csnk2a_ksr[!(p1s|p3s),]
csnk2a_ksr <- cbind(csnk2a_ksr, psite_no_heira)

# Construct the scoring function

source('match-tm.r')
csnk2_pwm <- makePWM(substr(psite_no_heira,2,14))

# Scoring function for the calculation of CK2 substrate quality

ED_weight <- function(psite,pwm) {
  
  neg_row <- apply(pwm[rownames(pwm) %in% c('D','E'),],2,sum)
  pwm <- pwm[!rownames(pwm) %in% c('D','E'),]
  pwm <- rbind(pwm,neg_row)
  rownames(pwm)[nrow(pwm)] <- 'DE'
  
  psite <- unlist(strsplit(psite,split=''))
  
  c=0
  min=0
  
  # Ignore the central residue
  for (i in c(1:6,8:13)) {
    
    aa <- psite[i]  
    if (aa %in% c('D','E')) {aa <- 'DE'}
    
    # Skip if the amino acid is not D or E
    if (!(aa %in% c('DE'))) {next}
    
    current <- pwm[rownames(pwm) %in% aa,i]
    c = c+current
  
  }
  
  maximum <- sum(pwm[rownames(pwm) == 'DE',][c(1:6,8:13)])
  mss = c/maximum
  
  return(unname(mss))
  
}

```

# The next step is to filter for CK2 target sites that fall in disordered regions. We will do this
# using an AlphaFold2-based assessment of protein disorder

```{r}

# AlphaFold disorder prediction on the basis of smoothened RSA (window size = 15)

AF2_accessibility <- readLines('9606.accessibility_windowed_scores.15.tdt')

AF2_vec <- NULL

count = 0

for (i in 1:nrow(csnk2a_ksr)) {
  
  print(i)
  
  accession <- csnk2a_ksr[i,3]
  pos <- csnk2a_ksr[i,4]
  
  grep_dex <- grep(accession,AF2_accessibility)
  
  # If we cannot find the corresponding residue in the accessibility file, then I will arbitrarily set
  # the disorder value to 0.5
  
  if (length(grep_dex) == 0) {disorder_pred <- 0.5; AF2_vec <- c(AF2_vec,disorder_pred); 
  count = count+1; next}
  
  disorder_pred <- AF2_accessibility[grep_dex]
  disorder_pred <- rapply(strsplit(disorder_pred,split='\t'), function(x) x[2])
  disorder_pred <- unlist(strsplit(disorder_pred,split=','))
  disorder_pred <- disorder_pred[pos]
  
  AF2_vec <- c(AF2_vec,disorder_pred)
  
}

AF2_vec <- as.numeric(AF2_vec)

# Now I will filter for phosphosites in disordered regions only
# For the cutoff, I will use the threshold that gives a 5% false discovery rate
# and 80% true positive rate

csnk2a_ksr_disorder <- csnk2a_ksr[which(AF2_vec >= 0.55),]
csnk2a_ksr_disorder <- cbind(csnk2a_ksr_disorder,AF2_vec[which(AF2_vec >= 0.55)])
colnames(csnk2a_ksr_disorder) <- c(colnames(csnk2a_ksr_disorder)[1:5],'sequence','AF2_disorder')

# Filter out redundant phosphosites assigned to the other catalytically active subunit

csnk2a_ksr_disorder_unique <- csnk2a_ksr_disorder[!duplicated(csnk2a_ksr_disorder[,6]),]

```

# Obtain list of all taxonomic divisions found in the data

```{r}

library(seqinr)

# Move to the directory containing all of the Ensembl orthologs where the spurious sequences have been removed by trimAl

setwd("vertebrate_ensembl_trimal_seq")

seq_files <- list.files()

# Fetch the names of the taxa (Ensembl annotation) for each orthologue

taxon_names_vec <- NULL

for (i in 1:length(seq_files)) {
  
  seq_file <- seqinr::read.fasta(seq_files[i],seqtype='AA')
  seq_file_names <- names(seq_file)
  taxon_names <- rapply(strsplit(seq_file_names,split='_'), function(x) x[length(x)])
  if(length(taxon_names) == 1) {next}
  taxon_names <- taxon_names[2:length(taxon_names)]
  taxon_names <- unique(taxon_names)
  taxon_names_vec <- c(taxon_names_vec, taxon_names)  
  
}

taxon_names_vec <- unique(taxon_names_vec)

# Manually arrange taxon names in chronological order

taxon_names_vec_ordered <- taxon_names_vec[c(9,10,11,3,18,20,19,21,1,14,4,15,5,7,16,17,8,6,13,2,12)]

# For each of the taxa we now need to (manually) give the divergence times obtained from TimeTree

taxon_names_vec_ordered_dates <- c(1105,824,684,615,473,435,413,352,312,177,159,105,96,90,74,67,43,29,20,16,9)
names(taxon_names_vec_ordered_dates) <- taxon_names_vec_ordered

# Place each age into one bin (>700mya, 200-700mya, <200mya)

taxon_names_vec_ordered_bins <- c('old','old','old','old','intermediate','intermediate',
                                  'intermediate','intermediate','intermediate',
                                  'young','young','young','young','young','young','young',
                                  'young','young','young','young','young')

names(taxon_names_vec_ordered_bins) <- taxon_names_vec_ordered

```

# Iterate through each one of the phosphsosites, and then estimate the timepoint at which the S emerged

```{r}

library(seqinr)
library(ape)

# Directory of filtered alignment files
filtered_alignment_files <- list.files('vertebrate_ensembl_trimal_seq')
# Directory of unfiltered alignment files
alignment_files <- list.files('vertebrate_ensembl_aligned')

phospho_taxon_vec <- NULL

tally = 0

for (i in 1:nrow(csnk2a_ksr_disorder_unique))  {
  
  print(i)
  
  # There are a a small number of orthologues
  # in primates that have identical sequences and therefore ASR does not work. We filter them out here.
  
  if (i %in% c(43,231,259,312)) {phospho_taxon_vec <- c(phospho_taxon_vec, 'NA'); next}
  
  phospho_taxon_oldest <- NULL
  
  accession <- csnk2a_ksr_disorder_unique[i,3]
  pos <- csnk2a_ksr_disorder_unique[i,4]
  
  # Retrieve the relevant sequence alignment
  
  filtered_alignment <- filtered_alignment_files[grep(accession,filtered_alignment_files)]
  
  # Skip if there were no filtered alignments for this accession
  
  if (length(filtered_alignment) == 0) {
    filtered_alignment <- alignment_files[grep(accession,alignment_files)]
    filtered_al_seq <- seqinr::read.fasta(paste('vertebrate_ensembl_aligned/',filtered_alignment,sep=''),seqtype='AA')
    
  } else {
  
    filtered_al_seq <- seqinr::read.fasta(paste('vertebrate_ensembl_trimal_seq/',filtered_alignment,sep=''),seqtype='AA')
    
  }
    
  # Skip if there is only one sequence
  
  if (length(filtered_al_seq) == 1) {phospho_taxon_vec <- c(phospho_taxon_vec, 'NA'); next}
  
  # First sequence is always human
  
  human_seq <- getSequence(filtered_al_seq[[1]])
  
  # Now map the human numbering to the alignment numbering
  
  count = 0
  al_pos_vec <- NULL
  human_pos_vec <- NULL
  
  for (j in 1:length(human_seq)) {
    
    aa <- human_seq[j]
    al_pos <- j
    
    if (aa != '-') {count=count+1; human_pos <- count}
    if (aa == '-') {count=count; human_pos <- '-'}
    
    al_pos_vec <- c(al_pos_vec, al_pos)
    human_pos_vec <- c(human_pos_vec, human_pos)
    
  }
  
  human_map_df <- data.frame(al_pos_vec, human_pos_vec,stringsAsFactors = FALSE)
  human_map_phospho_al <- human_map_df[human_map_df[,2] == pos,1]
  
  # Now read in the corresponding tree from FastML with ancestral sequence reconstructions
  
  filtered_al_tree_file <- paste('ASR_CK2/',accession,'/tree.newick.txt',sep='')
  filtered_al_tree <- ape::read.tree(filtered_al_tree_file)
  
  # N.B. Indices of the tips and nodes are given so that the tips is first, followed by the nodes
  tips <- filtered_al_tree$tip.label
  nodes <- filtered_al_tree$node.label
  
  # Obtain relevant tip/node indexes
  
  tip_dex <- which(tips==accession)
  root <- length(tips)+1
  
  # Path from root to accession tip
  
  accession_path <- nodepath(filtered_al_tree,from=root,to=tip_dex)
  
  # Remove the tip
  
  accession_path <- setdiff(accession_path,tip_dex)
  
  # Obtain the node indexes
  
  accession_path <- accession_path-length(tips)
  
  # Obtain internal path nodes
  
  path_nodes <- nodes[accession_path]
  
  # Path nodes from tip to root
  
  path_nodes <- rev(path_nodes)
 
  ############
  
  # Now, iterate through the nodes from tip to root to determine the first node that was not an S or T
  
  anc_seq_res_file <- paste('~/Documents/Work/CK2_MS/Figure_5/ASR_CK2/',accession,'/Ancestral_MaxMarginalProb_Char_Indel.txt',sep='')
  
  anc_seq_res <- read.table(anc_seq_res_file,head=T)
  anc_seq_res_pos <- anc_seq_res[anc_seq_res[,1] == human_map_phospho_al,]
  
  anc_aa_vec <- NULL
  
  for (j in 1:length(path_nodes)) {
    
    path_node <- path_nodes[j]
    
    anc_seq_res_pos_node <- anc_seq_res_pos[anc_seq_res_pos[,2] == path_node,]
    anc_seq_res_pos_node_aa <- anc_seq_res_pos_node[3]
    anc_seq_res_pos_node_aa <- as.character(unlist(unname(anc_seq_res_pos_node_aa)))
    
    anc_seq_res_pos_node_prob <- unlist(unname(anc_seq_res_pos_node[4]))
    
    # Consider the ancestral aa to be unknown if max probability < 0.5
    
    if (anc_seq_res_pos_node_prob < 0.5) {anc_seq_res_pos_node_aa <- '?'}
    names(anc_seq_res_pos_node_aa) <- path_node
    
    # Break the loop if the residue was not phosphorylatable
    if (!anc_seq_res_pos_node_aa %in% c('S','T')) {break}
    
    anc_aa_vec <- c(anc_aa_vec, anc_seq_res_pos_node_aa)
    
  } 
  
  # if the phosphosite is species-specific (skip the loop)
  if (length(anc_aa_vec) == 0) {phospho_taxon_vec <- c(phospho_taxon_vec, 'Human'); next}
  
  # Find the last node that is an S or T
  
  last_phospho <- anc_aa_vec[length(anc_aa_vec)]
  last_phospho_node <- names(last_phospho)
  last_phospho_node_index <- which(nodes == last_phospho_node)+length(tips)
  
  ## Now we need to find all tips arising from the node of interest
  
  global_path <- nodepath(filtered_al_tree,from=root)
  
  # Subset for paths that contain the node of interest
  phospho_paths <- global_path[grep(last_phospho_node_index,global_path)]
  
  # Retrieve the tip index for each path
  phospho_path_tips_index <- rapply(phospho_paths, function(x) x[length(x)])
  
  # Retrieve the tip for each path
  phospho_path_tips <- tips[phospho_path_tips_index]
  
  # Extract the taxa found across all relevant tips
  phospho_path_taxa <- rapply(strsplit(phospho_path_tips,split='_'), function(x) x[length(x)])
  
  # Retrieve the oldest taxon
  phospho_taxon_oldest <- taxon_names_vec_ordered[taxon_names_vec_ordered %in% phospho_path_taxa][1]
  
  phospho_taxon_vec <- c(phospho_taxon_vec, phospho_taxon_oldest)
  
}

### Add taxon information to the data frame of CK2 substrates

csnk2a_disorder_sites_dates <- data.frame(csnk2a_ksr_disorder_unique,phospho_taxon_vec)

# Retrieve the estimated ages for each phosphosite

phospho_taxon_vec_dates <- taxon_names_vec_ordered_dates[match(phospho_taxon_vec,names(taxon_names_vec_ordered_dates))]

# Separate the dates into 3 bins ('old','intermediate', and 'young')

phospho_taxon_vec_bin <- taxon_names_vec_ordered_bins[match(phospho_taxon_vec,names(taxon_names_vec_ordered_bins))]

# Append this information to the data frame

csnk2a_disorder_sites_dates <- data.frame(csnk2a_ksr_disorder_unique,phospho_taxon_vec,phospho_taxon_vec_dates, phospho_taxon_vec_bin)

```

# Score each one of the phosphosites with CK2 substrate quality scores

```{r}

# Discard sites that have a central T or hierarchical sites

filter_dex <- substr(csnk2a_disorder_sites_dates[,6],8,8) == 'S' & !substr(csnk2a_disorder_sites_dates[,6],9,9) %in% 'S' & !substr(csnk2a_disorder_sites_dates[,6],11,11) %in% 'S'

csnk2a_disorder_sites_dates_filtered <- csnk2a_disorder_sites_dates[filter_dex,]

# Calculate the CK2 substrate quality scores

sq_vec <- NULL

for (i in 1:nrow(csnk2a_disorder_sites_dates_filtered)) {
  
  psite <- as.character(csnk2a_disorder_sites_dates_filtered[i,6])
  psite <- substr(psite,2,14)
  sq <- ED_weight(psite, csnk2_pwm)
  
  sq_vec <- c(sq_vec,sq)
  
}

csnk2a_disorder_sites_dates_filtered_SQ <- data.frame(csnk2a_disorder_sites_dates_filtered,sq_vec)

# Remove NA values

csnk2a_ASR_df <- csnk2a_disorder_sites_dates_filtered_SQ[!is.na(csnk2a_disorder_sites_dates_filtered_SQ[,10]),]

```

# Generate the stacked barplot (substrate quality vs predicted age)

```{r}

# Set column names
colnames(csnk2a_ASR_df) <- c(colnames(csnk2a_ksr_disorder_unique),'taxon','age','age_bin','SQ')

col1 <- NULL
col2 <- NULL
col3 <- NULL

for (i in 0:7) {
  
  lower <- 0.1*i
  upper <- lower+0.1
  print(lower)
  print(upper)
  
  if(lower > 0.65) {upper <- 1.0}
  
  ED_rate <- csnk2a_ASR_df[csnk2a_ASR_df[,11] > lower & csnk2a_ASR_df[,11] <= upper,10]
  table(ED_rate)
  
  col3 <- c(col3,as.character(table(ED_rate)))
  col2 <- c(col2,names(table(ED_rate)))
  col1 <- c(col1,rep(paste(lower,'-',upper,sep=''),length(table(ED_rate))))
}

mss_data <- data.frame(col1,col2,col3,stringsAsFactors = FALSE)
mss_data[,1] <- as.factor(mss_data[,1])
mss_data[,2] <- as.factor(mss_data[,2])
mss_data[,3] <- as.numeric(mss_data[,3])
colnames(mss_data) <- c('SQ','Age','Count')

mss_data$Age <- factor(mss_data$Age, levels = c('young','intermediate','old'))

bin_count <- c(sum(mss_data[1:3,3]),sum(mss_data[4:6,3]),sum(mss_data[7:9,3]),sum(mss_data[10:12,3]),sum(mss_data[13:15,3]),sum(mss_data[16:18,3]),sum(mss_data[19:21,3]),sum(mss_data[22:24,3]))

bin_text <- c(rep('',2),bin_count[1],rep('',2),bin_count[2],rep('',2),bin_count[3],rep('',2),bin_count[4],rep('',2),bin_count[5],rep('',2),bin_count[6],rep('',2),bin_count[7],rep('',2),bin_count[8])

## Refine aesthetics using graphical parameters

p <- ggplot(mss_data, aes(fill=Age, y=Count, x=SQ)) + 
    geom_bar(position="fill", stat="identity",color='black',size=1)

p <- p+scale_fill_manual(values=c(colors()[109], colors()[121], colors()[132]))

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15),panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("Frequency") + xlab("Substrate quality") + ggtitle('')
p <- p+theme(axis.text=element_text(size=7),axis.title.x=element_text(size=11,face="bold"),axis.title.y=element_text(size=11,face="bold"),plot.title=element_text(size=18,face='bold'))

p <- p + theme(legend.title = element_text(size=9.5), legend.text = element_text(size=8))

p <- p+geom_text(data=mss_data, aes(x=SQ),y=rep(1.025,24),label=bin_text,col='black', fontface='plain', size=3.6)

ggsave(file='Figure_4b.pdf', plot=p, width=5.5, height=4.8)

```
