---
title: "Figure_2"
author: "David Bradley"
date: "10/1/2020"
output: html_document
---

# GGplot font

```{r}

# https://stackoverflow.com/questions/27689222/changing-fonts-for-graphs-in-r

library(extrafont)

font_import()
loadfonts()       #Register fonts for Windows bitmap output
fonts() 

```

# Read in data

```{r}

Ishi_disorder_scaled <- readRDS('Ishi_disorder_CK2_github.rds')

```


# Supplementary figure 2A (start by using results from supplementary figure 2)

```{r}

abundance_list <- list()
col1 <- NULL
col2 <- NULL
col3 <- NULL

for (i in 1:9) {
  
  lower <- (0.5*i)-1
  upper <- (0.5*i)-0.5
  print(lower)
  print(upper)
  
  abundance_stoi <- Ishi_disorder_scaled[Ishi_disorder_scaled[,6] > lower & Ishi_disorder_scaled[,6] <= upper,3]
  abundance_stoi <- abundance_stoi[!abundance_stoi == 'NaN']
  abundance_list <- c(abundance_list, list(abundance_stoi))
  
  col1 <- c(col1,abundance_stoi)
  col2 <- c(col2,rep(paste(lower,'-',upper,sep=''),length(abundance_stoi)))
}

mss_data <- cbind(col1,col2)
mss_data <- data.frame(mss_data,stringsAsFactors = FALSE)
mss_data[,1] <- as.numeric(mss_data[,1])
mss_data[,2] <- as.factor(mss_data[,2])
colnames(mss_data) <- c('Stoichiometry','Positions')

p <- ggplot(mss_data, aes(x=Positions, y=Stoichiometry)) + geom_boxplot(fill='white',color=colors()[132], lwd=1.15, notch=FALSE,fatten=0.75, outlier.shape=NA) + geom_jitter(width = 0.1, color=colors()[132],size=0.4) #colors()[258]

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("CK2 Stoichiometry") + xlab("Abundance (log10 ppm)") + ggtitle('')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p + theme(axis.title.x = element_text(vjust=1.5))

p <- p+theme(axis.text.x=element_text(size=6),axis.text.y=element_text(size=8),axis.title.x=element_text(size=9,face="plain",vjust=4.5),axis.title.y=element_text(size=9,face="plain",vjust=-3),plot.title=element_text(size=18,face='bold'))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(panel.border= element_blank())
p <- p + theme(plot.margin = unit(c(0,0,0.1,0), "cm")) # t, r, b, l
p <- p + theme(axis.text.x = element_text(angle = 30, vjust = 1.0, hjust=1))
a <- p
a

```

# Supplementary figure 2B (disorder)

```{r}

disorder_list <- list()
col1 <- NULL
col2 <- NULL
col3 <- NULL

for (i in 1:11) {
  
  lower <- (0.1*i)-0.2
  upper <- (0.1*i)-0.1
  print(lower)
  print(upper)
  
  disorder_stoi <- Ishi_disorder_scaled[Ishi_disorder_scaled[,10] > lower & Ishi_disorder_scaled[,10] <= upper,3]
  disorder_stoi <- disorder_stoi[!disorder_stoi == 'NaN']
  disorder_list <- c(disorder_list, list(disorder_stoi))
  
  col1 <- c(col1,disorder_stoi)
  col2 <- c(col2,rep(paste(lower,'-',upper,sep=''),length(disorder_stoi)))
}

mss_data <- cbind(col1,col2)
mss_data <- data.frame(mss_data,stringsAsFactors = FALSE)
mss_data[,1] <- as.numeric(mss_data[,1])
mss_data[,2] <- as.factor(mss_data[,2])
colnames(mss_data) <- c('Stoichiometry','Positions')

p <- ggplot(mss_data, aes(x=Positions, y=Stoichiometry)) + geom_boxplot(fill='white',color=colors()[132], lwd=1.15, notch=FALSE,fatten=0.75, outlier.shape=NA) + geom_jitter(width = 0.1, color=colors()[132],size=0.4) #colors()[258]

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("") + xlab("Disorder") + ggtitle('')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p + theme(axis.title.x = element_text(vjust=1.5))

p <- p+theme(axis.text.x=element_text(size=6),axis.text.y=element_text(size=8),axis.title.x=element_text(size=9,face="plain",vjust=4.5),axis.title.y=element_text(size=8,face="plain"),plot.title=element_text(size=18,face='bold'))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(panel.border= element_blank())
p <- p + theme(plot.margin = unit(c(0,0,0.1,0), "cm")) # t, r, b, l
p <- p + theme(axis.text.x = element_text(angle = 30, vjust = 1.0, hjust=1))
b <- p
b

```

# Supplementary figure 2C (subcellular localisation)

```{r}

Ishi_disorder_scaled$Location <- factor(Ishi_disorder_scaled$Location, levels = c('Other','C','NC','N'))

p <- ggplot(Ishi_disorder_scaled, aes(x=Location, y=Stoichiometry)) + geom_boxplot(fill='white',color=colors()[190], lwd=1.25, notch=FALSE,fatten=1.00, width=0.65,outlier.shape=NA) + geom_jitter(width = 0.2, color=colors()[132],size=0.4,alpha=0.45) #colors()[123]

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("") + xlab("Subcellular location") + ggtitle('')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text=element_text(size=8),axis.title=element_text(size=9,face="plain"),plot.title=element_text(size=10,face='bold'))
p <- p + theme(panel.border= element_blank())
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0.2,0,0.1,0), "cm")) # t, r, b, l
c <- p

c

```

# Supplementary figure 2D (interaction number)

```{r}

Ishi_disorder_scaled[Ishi_disorder_scaled$Int_num > 1,8] <- 1

Ishi_disorder_scaled[Ishi_disorder_scaled$Int_num == 0,8] <- 'N'
Ishi_disorder_scaled[Ishi_disorder_scaled$Int_num == 1,8] <- 'Y'

Ishi_disorder_scaled$Int_num <- factor(Ishi_disorder_scaled$Int_num, levels = c('N','Y'))

p <- ggplot(Ishi_disorder_scaled, aes(x=Int_num, y=Stoichiometry)) + geom_boxplot(fill='white',color=colors()[190], lwd=1.25, notch=FALSE,fatten=1.00, outlier.shape=NA,width=0.65) + geom_jitter(width = 0.2, color=colors()[132],size=0.4,alpha=0.45) #colors()[123]

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("") + xlab("Reported \ninteraction") + ggtitle('')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text=element_text(size=8),axis.title=element_text(size=9,face="plain"),plot.title=element_text(size=10,face='bold'))
p <- p + theme(panel.border= element_blank())
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0.2,0,0.1,0), "cm")) # t, r, b, l
d <- p

d

```

# Supplementary figure 2E (Phosphoacceptor)

```{r}

Ishi_disorder_scaled$Phosphoacceptor <- factor(Ishi_disorder_scaled$Phosphoacceptor, levels = c('T','S'))

p <- ggplot(Ishi_disorder_scaled, aes(x=Phosphoacceptor, y=Stoichiometry)) + geom_boxplot(fill='white',color=colors()[190], lwd=1.25, notch=FALSE,fatten=1.00, outlier.shape=NA,width=0.565) + geom_jitter(width = 0.2, color=colors()[132],size=0.4, alpha=0.45) #colors()[123]

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("") + xlab("Phosphoacceptor") + ggtitle('')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text=element_text(size=8),axis.title=element_text(size=7.5,face="plain"),plot.title=element_text(size=10,face='bold'))
p <- p + theme(panel.border= element_blank())
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0.2,0,0.1,0), "cm")) # t, r, b, l
e <- p

e

```

# Supplementary figure 2F (abundance:substrate_quality)

```{r}

# We need to construct a new data frame to capture the interaction

Ishi_A_C <- Ishi_disorder_scaled
Ishi_A_median <- median(Ishi_disorder_scaled$Abundance)
Ishi_C_median <- median(Ishi_disorder_scaled$Charge)

A_C_vec <- NULL

for (i in 1:nrow(Ishi_A_C)) {
  
  stoi_row <- Ishi_A_C[i,]
  
  if (stoi_row$Abundance < Ishi_A_median & stoi_row$Charge < Ishi_C_median) {A_C <- 'Low A Low S'}
  if (stoi_row$Abundance < Ishi_A_median & stoi_row$Charge > Ishi_C_median) {A_C <- 'Low A High S'}
  if (stoi_row$Abundance > Ishi_A_median & stoi_row$Charge < Ishi_C_median) {A_C <- 'High A Low S'}
  if (stoi_row$Abundance > Ishi_A_median & stoi_row$Charge > Ishi_C_median) {A_C <- 'High A High S'}
  
  A_C_vec <- c(A_C_vec, A_C)
  
}

Ishi_A_C <- cbind(Ishi_A_C, A_C_vec)
colnames(Ishi_A_C) <- c(colnames(Ishi_disorder_scaled), 'AC')

Ishi_A_C$AC <- factor(Ishi_A_C$AC, levels = c('High A Low S','High A High S','Low A Low S','Low A High S'))

p <- ggplot(Ishi_A_C, aes(x=AC, y=Stoichiometry)) + geom_boxplot(fill='white',color=colors()[190], lwd=1.25, notch=FALSE,fatten=1.05,outlier.shape = NA,width=0.55) + geom_jitter(width = 0.2, color=colors()[601],size=0.75,alpha=0.55) #colors()[123]

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("CK2 Stoichiometry") + xlab("Abundance : Substrate quality") + ggtitle('')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text.y=element_text(size=8),axis.text.x=element_text(size=5.5),axis.title.x=element_text(size=8,face="plain",vjust=2.25),
             axis.title.y=element_text(size=9,face="plain"),plot.title=element_text(size=9,face='bold'))
p <- p + theme(panel.border= element_blank())
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0.2,0.5,0.1,0.5), "cm")) # t, r, b, l
f <- p
f

```

# Supplementary figure 2G (Interaction:substrate_quality)

```{r}

# We need to construct a new data frame to capture the interaction

Ishi_I_C <- Ishi_disorder_scaled
Ishi_C_median <- median(Ishi_disorder_scaled$Charge)

I_C_vec <- NULL

for (i in 1:nrow(Ishi_I_C)) {
  
  stoi_row <- Ishi_I_C[i,]
  
  if (stoi_row$Int_num == 'Y' & stoi_row$Charge < Ishi_C_median) {I_C <- 'I Low S'}
  if (stoi_row$Int_num == 'Y'  & stoi_row$Charge > Ishi_C_median) {I_C <- 'I High S'}
  if (stoi_row$Int_num == 'N'  & stoi_row$Charge < Ishi_C_median) {I_C <- 'No I Low S'}
  if (stoi_row$Int_num == 'N' & stoi_row$Charge > Ishi_C_median) {I_C <- 'No I High S'}
  
  I_C_vec <- c(I_C_vec, I_C)
  
}

Ishi_I_C <- cbind(Ishi_I_C, I_C_vec)
colnames(Ishi_I_C) <- c(colnames(Ishi_disorder_scaled), 'IC')

Ishi_I_C$IC <- factor(Ishi_I_C$IC, levels = c('No I Low S','No I High S','I Low S','I High S'))

p <- ggplot(Ishi_I_C, aes(x=IC, y=Stoichiometry)) + geom_boxplot(fill='white',color=colors()[190], lwd=1.25, notch=FALSE,fatten=1.05, outlier.shape = NA, width=0.55) + geom_jitter(width = 0.2, color=colors()[601],size=0.75, alpha=0.55) #colors()[123]

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("") + xlab("Interaction : Substrate quality") + ggtitle('')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text.y=element_text(size=8),axis.text.x=element_text(size=6),axis.title.x=element_text(size=8,face="plain",vjust=2.25),
             axis.title.y=element_text(size=8,face="plain"),plot.title=element_text(size=9,face='bold'))
p <- p + theme(panel.border= element_blank())
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0.2,0.25,0.1,0.25), "cm")) # t, r, b, l
g <- p
g

```

# Supplementary figure 2H (Disorder:phosphoacceptor)

```{r}

# We need to construct a new data frame to capture the interaction

Ishi_D_P <- Ishi_disorder_scaled

D_P_vec <- NULL

for (i in 1:nrow(Ishi_D_P)) {
  
  stoi_row <- Ishi_D_P[i,]
  
  if (stoi_row$Disorder_class == 'O' & stoi_row$Phosphoacceptor == 'T') {D_P <- 'Order T'}
  if (stoi_row$Disorder_class == 'D' & stoi_row$Phosphoacceptor == 'T') {D_P <- 'Disorder T'}
  if (stoi_row$Disorder_class == 'O' & stoi_row$Phosphoacceptor == 'S') {D_P <- 'Order S'}
  if (stoi_row$Disorder_class == 'D' & stoi_row$Phosphoacceptor == 'S') {D_P <- 'Disorder S'}
  
  D_P_vec <- c(D_P_vec, D_P)
  
}

Ishi_D_P <- cbind(Ishi_D_P, D_P_vec)
colnames(Ishi_D_P) <- c(colnames(Ishi_disorder_scaled), 'IC')

Ishi_D_P$IC <- factor(Ishi_D_P$IC, levels = c('Order T','Disorder T','Order S','Disorder S'))

p <- ggplot(Ishi_D_P, aes(x=IC, y=Stoichiometry)) + geom_boxplot(fill='white',color=colors()[190], lwd=1.25, notch=FALSE,fatten=1.05, outlier.shape = NA, width=0.55) + geom_jitter(width = 0.2, color=colors()[601],size=0.75, alpha=0.55) #colors()[123]

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("") + xlab("Disorder : Phosphoacceptor") + ggtitle('')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text.y=element_text(size=8),axis.text.x=element_text(size=6),axis.title.x=element_text(size=8,face="plain",vjust=2.25),
             axis.title.y=element_text(size=8,face="plain"),plot.title=element_text(size=9,face='bold'))
p <- p + theme(panel.border= element_blank())
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0.2,0.5,0.1,0.5), "cm")) # t, r, b, l
h <- p
h

```

# Calcuate the p-values for the CK2 data

```{r}

Ishi_disorder_scaled[,3] <- Ishi_disorder_scaled[,3] / 100

# Disorder

model_disorder_score <- glm(Stoichiometry ~ Disorder_score, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))
model_null <- glm(Stoichiometry ~ 1, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

disorder_score_F_p_AF2 <- anova(model_null,model_disorder_score, test='F')$'Pr(>F)'[2]

# Substrate quality

model_charge <- glm(Stoichiometry ~ Charge, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))
model_null <- glm(Stoichiometry ~ 1, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

charge_F_p <- anova(model_null,model_charge, test='F')$'Pr(>F)'[2]

# Abundance

model_abundance <- glm(Stoichiometry ~ Abundance, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))
model_null <- glm(Stoichiometry ~ 1, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

abundance_F_p <- anova(model_null,model_abundance, test='F')$'Pr(>F)'[2]

# Phoshoacceptor

model_phosphoacceptor <- glm(Stoichiometry ~ Phosphoacceptor, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))
model_null <- glm(Stoichiometry ~ 1, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

phosphoacceptor_class_F_p <- anova(model_null,model_phosphoacceptor, test='F')$'Pr(>F)'[2]

# Subcellular location

model_location <- glm(Stoichiometry ~ Location, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))
model_null <- glm(Stoichiometry ~ 1, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

location_F_p <- anova(model_null,model_location, test='F')$'Pr(>F)'[2]

# Physical interaction

model_physical <- glm(Stoichiometry ~ Int_num, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))
model_null <- glm(Stoichiometry ~ 1, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

physical_F_p <- anova(model_null,model_physical, test='F')$'Pr(>F)'[2]

# Charge:abundance

model_charge_abundance <- glm(Stoichiometry ~ Charge+Abundance, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

model_charge_abundance_int <- glm(Stoichiometry ~ Charge+Abundance+Charge:Abundance, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

charge_abundance_int_F_p <- anova(model_charge_abundance,model_charge_abundance_int, test='F')$'Pr(>F)'[2]

# Disorder:phosphoacceptor

model_charge_phosphoacceptor <- glm(Stoichiometry ~ Disorder_score+Phosphoacceptor, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

model_charge_phosphoacceptor_int <- glm(Stoichiometry ~ Disorder_score+Phosphoacceptor+Disorder_score:Phosphoacceptor, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

disorder_phosphoacceptor_p <- anova(model_charge_phosphoacceptor,model_charge_phosphoacceptor_int, test='F')$'Pr(>F)'[2]

# Charge:physical interaction

model_charge_physical <- glm(Stoichiometry ~ Charge+Int_num, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

model_charge_physical_int <- glm(Stoichiometry ~ Charge+Int_num+Charge:Int_num, data = Ishi_disorder_scaled, family=quasibinomial(cloglog))

charge_physical_int_F_p <- anova(model_charge_physical,model_charge_physical_int, test='F')$'Pr(>F)'[2]

```


# Supplementary figure 2I

```{r}

p_values <- c(disorder_score_F_p_AF2,charge_F_p,abundance_F_p,phosphoacceptor_class_F_p,location_F_p,physical_F_p,
              charge_abundance_int_F_p,disorder_phosphoacceptor_p, charge_physical_int_F_p)
min_log10_p <- -log(p_values,base=10)

predictors <- c('Predicted disorder','Substrate quality (SQ)','Abundance','Phosphoacceptor','Subcellular location','Interaction',
                'Abundance : SQ', 'Disorder : Phosphoacceptor', 'Interaction : SQ')

df_pvalues <- data.frame(predictors,min_log10_p)
colnames(df_pvalues) <- c('Predictors','Pvalue')
df_pvalues$Predictors <- factor(df_pvalues$Predictors , levels = rev(c('Predicted disorder','Substrate quality (SQ)','Abundance','Phosphoacceptor','Interaction','Subcellular location','Abundance : SQ',
    'Interaction : SQ','Disorder : Phosphoacceptor')))

p <- ggplot(data=df_pvalues, aes(x=Predictors, y=Pvalue)) +
  geom_bar(stat="identity",fill=colors()[35],color='black',lwd=1)

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("-log10(P)") + xlab("") + ggtitle('CK2')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text=element_text(size=6),axis.title=element_text(size=6,face="plain",vjust=0),plot.title=element_text(size=10,face='bold',vjust=-1.5))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0,0.1,0,-0.35), "cm")) # t, r, b, l

# Horizontal bar plot
p <- p + coord_flip()
p <- p+theme(axis.title.x=element_text(size=9,face="plain",vjust=5))
i <- p
i

```

# Supplementary figure 2J (from MAPK analysis)

```{r}

p_values <- c(disorder_score_F_p_MAPK,motif_F_p_MAPK,abundance_F_p_MAPK,phosphoacceptor_class_F_p_MAPK,location_F_p_MAPK,physical_F_p_MAPK, charge_abundance_int_F_p_MAPK,disorder_phosphoacceptor_p_MAPK, charge_physical_int_F_p_MAPK)
min_log10_p <- -log(p_values,base=10)

predictors <- c('Predicted disorder','Substrate quality (SQ)','Abundance','Phosphoacceptor','Subcellular location','Interaction',
                'Abundance : SQ', 'Disorder : Phosphoacceptor', 'Interaction : SQ')

df_pvalues <- data.frame(predictors,min_log10_p)
colnames(df_pvalues) <- c('Predictors','Pvalue')
df_pvalues$Predictors <- factor(df_pvalues$Predictors , levels = rev(c('Predicted disorder','Substrate quality (SQ)','Abundance','Phosphoacceptor','Interaction','Subcellular location','Abundance : SQ',
    'Interaction : SQ','Disorder : Phosphoacceptor')))

p <- ggplot(data=df_pvalues, aes(x=Predictors, y=Pvalue)) +
  geom_bar(stat="identity",fill=colors()[147],color='black',lwd=0.75)

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("-log10(P)") + xlab("") + ggtitle('MAPK')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text=element_text(size=6),axis.title=element_text(size=6,face="plain",vjust=0),plot.title=element_text(size=10,face='bold',vjust=-1.5))
#p <- p + coord_cartesian(ylim = c(0, 30))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0,0.1,0,-0.35), "cm")) # t, r, b, l

# Horizontal bar plot
p <- p + coord_flip(ylim = c(0, 22))
p <- p+theme(axis.title.x=element_text(size=9,face="plain",vjust=5))
j <- p
j

```

# Supplementary figure 2K (from EGFR analysis)

```{r}

p_values <- c(disorder_score_F_p_EGFR_AF2,motif_F_p_EGFR,abundance_F_p_EGFR,phosphoacceptor_class_F_p_EGFR,location_F_p_EGFR,physical_F_p_EGFR, motif_abundance_int_F_p_EGFR, disorder_phosphoacceptor_p_EGFR, charge_physical_int_F_p_EGFR)
min_log10_p <- -log(p_values,base=10)

predictors <- c('Predicted disorder','Substrate quality (SQ)','Abundance','Phosphoacceptor','Subcellular location','Interaction',
                'Abundance : SQ', 'Disorder : Phosphoacceptor', 'Interaction : SQ')

df_pvalues <- data.frame(predictors,min_log10_p)
colnames(df_pvalues) <- c('Predictors','Pvalue')
df_pvalues$Predictors <- factor(df_pvalues$Predictors , levels = rev(c('Predicted disorder','Substrate quality (SQ)','Abundance','Phosphoacceptor','Interaction','Subcellular location','Abundance : SQ',
    'Interaction : SQ','Disorder : Phosphoacceptor')))

p <- ggplot(data=df_pvalues, aes(x=Predictors, y=Pvalue)) +
  geom_bar(stat="identity",fill=colors()[548],color='black',lwd=0.75)

# Font
p <- p+theme_bw() + theme(text=element_text(family="Ubuntu Light", face="plain", size=15))

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")) )

p <- p + ylab("-log10(P)") + xlab("") + ggtitle('EGFR')
p <- p + theme(axis.title.y = element_text(vjust=-1.5))
p <- p+theme(axis.text=element_text(size=6),axis.title=element_text(size=6,face="plain",vjust=0),plot.title=element_text(size=10,face='bold',vjust=-1.5))
#p <- p + coord_cartesian(ylim = c(0, 30))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none") # axis.line = element_blank(), panel.border = element_blank()) 
p <- p + theme(plot.margin = unit(c(0,0.1,0,-0.35), "cm")) # t, r, b, l

# Horizontal bar plot
p <- p + coord_flip(ylim = c(0, 22))
p <- p+theme(axis.title.x=element_text(size=9,face="plain",vjust=5))
k <- p
k

```


# Cowplot (put it all together)

```{r}

library(cowplot)

g1 <- plot_grid(a,b,c,d,e,ncol=5,nrow=1,align='h',rel_widths=c(0.33,0.33,0.25,0.2,0.225), labels=c('A','B','C','D','E'), axis='b')
g1

g2 <- plot_grid(f,g,h,ncol=3,nrow=1,align='h',rel_widths=c(0.38,0.3333,0.33333), labels=c('F','G','H'), axis='b')
g2

g3 <- plot_grid(i,j,k,ncol=3,nrow=1,align='h',rel_widths=c(0.3333,0.3333,0.33333), labels=c('I','J','K'), axis='b')
g3

g4 <- plot_grid(g1,g2,g3,nrow=3)
g4

ggsave(file='/home/david/Documents/Work/CK2_revisions/Figure_2/Figure_2.pdf', plot=g4, width=8.5, height=6.25)

```
  




